%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{The electricity model}
\label{sec:}

This is the detailed documentation, file by file of the Swiss electricity market model.

%%%%%%%%%%%%
\subsection{run\_elec.py}

This is the file that is used to the electricity model. It has for input the duration of the runs in years. It then initialise the electricity model.

The script is using a loop where each iteration is one year. This is the \texttt{step()} function of the \texttt{model\_elec.py} file.

For checks, some of the results can be plotted every five years.

Once the simulation has ended, the data is extracted from the \texttt{datacollector} and save as a \texttt{.csv} file.

%%%%%%%%%%%% end of run\_elec.py


%%%%%%%%%%%%
\subsection{model\_elec.py}

This script is composed of two main parts: the \texttt{get\_supply} functions at the beginning and the \texttt{class Electricity(Model)}. The functions are there for the datacollector. They are used to collect the data that needs to be saved from the model. They are outside of the class and only called by the datacollector following the architecture provided by mesa. Each of the functions returns what needs to be recorded and only that.

The \texttt{class Electricity(Model)} begins with the initialisation of all the parameters that are needed for the simulation of the electricity model. This is detailed within the python file itself and is not detailed here.

The functions:

\begin{itemize}
\item \texttt{policy\_implementation()}

This function is used exclusively for the hybrid model. It implements whichever policy has been chosen by the policy makers through a modification of a number of pre-defined parameters. This function is not used when the electricity model is run alone.

\item \texttt{step()}

This function is used to simulate one year of the policy process. It includes the implementation of the policies, the iteration over 8760 hours and the calculation of the KPIs needed for the hybrid model at the end. The function returns the KPIs.

\item \texttt{step\_hourly()}

This is the main function of the electricity model. It does whatever needs to be run over an hour. This includes the merit-order curve construction and the selection of the point of supply and demand, it includes the investment of the actors and it includes all of the recording of the data points within the model.

For the merit order curve: first the supply list is built, this is followed by the construction of the demand list. The point at which these cross is then calculated. Once it has been found, the electricity supplied is allocated to the different assets along with the amount of electricity. This is also true for the demand for the asset that have a certain demand.

The first part of the merit curve is to construct the supply list. This list is composed of all of the assets and the supply they can provide and at what price. This calculate for each asset depending on the technology considered. The list is then sorted by prices which the assets that offer supply at the lower price at the front of the list and the most expensive ones at the end. This also includes a probability that certain assets will go offline due to unexpected maintenance.

The same is then done for the demand list. But the list is ordered in the opposite sense with the highest demand prices at the front of the list and the lowest at the back. The demand list is only made of the inelastic demand, the demand from bordering countries and the demand from hydro power plants.

Then, there is a need to find at which point the two list cross. That is when the demand meets the supply at the same price. This is done using an algorithm that runs through each of the lists. Every time the supply has been allocated to demand, supply of a new asset is added and vice versa. This algorithm also takes into account that capacity allocated from France through the NTC or LTC needs to add up to the total of the border capacity and not go over that limit. This results is dynamically adjusting the supply and demand lists as supply and demand are allocated.

In some instances, when there is not enough supply to meet the inelastic demand, it is possible for there to be a blackout.

Once the point where supply meets demand has been found, the algorithm stop and the electricity price for that specific hour has been defined. The supply is allocated to the different assets along with the demand. This allows for the calculation of the utilisation factor of the different technologies later on. The revenue per assets are also attributed.

After the merit-order curve come the so-called end of step actions. This lumps all of the other actions that can be performed in a step. It includes mandatory actions along with opportunity actions (such as investments).

These include:

	\begin{itemize}
	\item Nuclear asset maintenance
	\item Asset ageing: simple iteration of one year for the age parameter for all assets
	\item Investment algorithms: investors must decide whether they want to invest in new assets or not
	\item End of life actions for assets: potential decommissioning, mothballing or re-investment in assets.
	\item Planned assets actions: assets that are already planned need to be advanced in their steps, either constructed or put on hold.
	\end{itemize}

\item \texttt{hydro\_demand\_supply\_check}

This is a function that is used to reset the hydro supply or demand if it is already supplying or demanding. This is done to avoid having a hydro pumping plant both providing and supplying. This only affect hydro pumping assets.

\item \texttt{end\_of\_life}

This function is used to perform the so-called end of life actions. This is divided in two parts. For the long term contracts, if they come to the end of their life they are decommissioned and put off line.

For the nuclear, wind, solar and CCGT assets, if these assets are within ten years of their end of life, it consists of checking if the asset is profitable. This calls the next function with different actions depending on the profitability of the asset. If the asset is already mothballed, then a different set of profitability checks are performed.

\item \texttt{end\_of\_life\_profitability}

This function is used to assess the profitability of plants at their of life and perform the necessary actions based on the results of this profitability.

First one year and five year profitability are calculated. Based on the results of these calculations, actions are taken.

	\begin{itemize}
	\item If the one year profitability is negative and the age of the asset is past its maximum lifetime, the asset is decommissioned.
	\item If the one year profitability is negative but the five year is positive and the asset is not past its lifetime, the asset is mothballed.
	\item If the one year profitability is positive and the asset is not past its lifetime:
		\begin{itemize}
		\item If the the asset has not yet been renovated, it is renovated and its life is extended by five years.
		\item If the asset has already been renovated too much, it is decommissioned.
		\end{itemize}
	\end{itemize}

\item \texttt{asset\_decommissioning}

This function remove the asset that has been decommissioned from the asset schedule. Additionally, if the asset is a solar or a wind asset, then the utilisation factor potential for these assets is recalculated.

\item \texttt{asset\_mothball}

This function mothballs an asset. It puts it offline and extends its overall lifetime by one year.

\item \texttt{asset\_demothball}

This function puts back online assets that have been mothballed.

\item \texttt{saving\_supply}



\item \texttt{saving\_demand}
\item \texttt{planned\_assets\_invest}
\item \texttt{elec\_UF\_updates}
\item \texttt{pp\_investment\_recording}
\item \texttt{pp\_supply\_recording}
\item \texttt{parameter\_update\_yearly}
\item \texttt{parameter\_update\_hourly}
\item \texttt{pp\_KPI\_calculation}
\item \texttt{calculation\_solar\_UF\_potential}
\item \texttt{calculation\_wind\_UF\_potential}
\item \texttt{get\_supply}
\end{itemize}


%%%%%%%%%%%% end of model\_elec.py

%%%%%%%%%%%%
\subsection{asset.py}

This file is used to redefine the asset class. It copies and modifies the \texttt{Asset} class from mesa (former \texttt{Agent} class) and introduces the \texttt{AssetWCost} class for as a subclass of it. The new class is introduced for assets for which costs are needed and are present in the calculations. This consists of all assets except for the \texttt{LTContract} and \texttt{NTCAsset}.

There are no functions that are used at this level of the \texttt{Asset}.

%%%%%%%%%%%% end of asset.py

%%%%%%%%%%%%
\subsection{model\_elec\_agents.py}


%%%%%%%%%%%% end of model\_elec\_agents.py

%%%%%%%%%%%%
\subsection{model\_elec\_assets.py}


%%%%%%%%%%%% end of model\_elec\_assets.py

%%%%%%%%%%%%
\subsection{model\_elec\_agents\_init.py}


%%%%%%%%%%%% end of model\_elec\_agents\_init.py

%%%%%%%%%%%%
\subsection{model\_elec\_assets\_init.py}


%%%%%%%%%%%% end of model\_elec\_assets\_init.py



\begin{verbatim}
Text enclosed inside \texttt{verbatim} environment 
is printed directly 
and all \LaTeX{} commands are ignored.
\end{verbatim}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%